\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(d3).

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}

For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.

Since $f(n) = \Theta(n^k)$, we must have $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ for $n \geq n_0$ and $c_1, c_2$ for $c_1, c_2 \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:

\begin{gather}
    0 \leq c_1 (2n)^k \leq f(2n) \leq c_2 (2n)^k \nonumber \\
    \Rightarrow 0 \leq c_1 \cdot 2^k \cdot n^k \leq f(2n) \leq c_2 \cdot 2^k \cdot n^k
\end{gather}

From $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ , we may also infer:

\begin{gather}
    \frac{f(n)}{c_1} \geq k \geq \frac{f(n)}{c_2} \\
    \Rightarrow c_1 \cdot 2^k \cdot \frac{f(n)}{c_2} \leq f(2n) \leq c_2 \cdot 2^k \cdot \frac{f(n)}{c_1} \\
    \Rightarrow 0\leq c^{'}_{1}\cdot f(n) \leq f(2n) \leq c^{'}_{2}\cdot f(2n) \ \ \ \text{for}\begin{cases}
                    c^{'}_{1} = \frac{c_1 \cdot 2^k}{c_2} \\
                    c^{'}_{2} = \frac{c_2 \cdot 2^k}{c_1}
                \end{cases}
\end{gather}

Thus we may conclude if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
